The \kepler Smear Campaign I: An Asteroseismic Catalogue of Bright Red Giants

### 2018-09-06 paper/ms.tex
some edits

% Beyond searching for planets, 
\kepler has revolutionized the field of asteroseismology for solar-like oscillations \citep{2010PASP..122..131G}. It has yielded the first detection of gravity-mode period spacings in a red giant \citep{rggmodes}, enabling probes of interior rotation of red giants \citep{rggmoderotation} and distinguishing between hydrogen- and helium-burning cores \citep{rggmodehelium}. It has also permitted the determination of ages and fundamental parameters of main-sequence stars as cool as the Sun and hotter \citep{silvaages}, including planet-hosting stars \citep{huberplanetages,silvaplanetages,2018MNRAS.479.4786V}, revealing the most ancient known planetary system, dating back to the earliest stages of the galaxy \citep{ancientplanets}. By comparing asteroseismic stellar ages to stellar rotation periods, \citet{angusgyro} have shown that gyrochronology models cannot fit the data with a single relation, leading \citet{vansadersgyro} to suggest a qualitative change in dynamo mechanism as stars age through the main sequence. \newpage

@@

In \citet{smear}, we demonstrated a method for extracting precise light curves of bright stars in \kepler and K2, and presented light curves of a small number of variable stars as examples to illustrate this method. In this paper we present smear light curves of all unobserved or significantly under-observed stars brighter than $Kp=9$ in the \kepler field. This sample mostly consists of red giants and hot stars, containing only a few FG dwarfs. We find no transiting planets, but detect \textcolor{red}{$M$}~new eclipsing binaries, and measure solar-like oscillations in 34~red giants. We do not model hot stars or FG dwarfs in great detail, but provide some discussion and initial classification of interesting variability. For eclipsing binaries, we present the results of light-curve modelling to precisely determine their parameters. For the oscillating red giants that constitute the bulk of the sample, we determine the asteroseismic parameters \numax and \Dnu, and therefore stellar masses and \logg measurements; and we and obtain high-resolution spectroscopy with the Tillinghast Reflector \'{E}chelle Spectrograph (TRES), from whose spectra we derive stellar parameters and elemental abundances constrained by asteroseismic parameters. These asteroseismic constraints can be compared to those from \gaia, offering the opportunity both to test asteroseismic scaling relations and combine both datasets to refine the benchmark star properties further.

@@

Because the smear data are collected along an entire CCD~column, there is the risk of contamination from sufficiently bright sources. This is especially true in doing asteroseismology of red giants, where the low-amplitude stochastically-excited oscillations can be washed out in a power spectrum by the coherent high amplitude variations of a classical pulsator, even if the background star is much fainter. We can assess the importance of this contamination by considering the differences between odd and even quarters: because the \kepler spacecraft rotates $90^{\circ}$ between successive quarters, any contaminant will lie in the same column as a smear target only every second quarter, falling in the other quarters in the same row but not necessarily the same column. We have therefore generated Lomb-Scargle periodograms \citep{lomb,scargle} of each light curve, clipped for outliers, and considering only odd and even quarters, and visually inspected these for significant differences. In the great majority of cases they closely resemble one another, indicating that contamination is at worst a minor effect. In the case of HD~181878, a red giant, there is clear and significant contamination from an M~giant, as is seen in Figure~\ref{contamination}.

>>>>

% Beyond searching for planets, 
\kepler has revolutionized the field of asteroseismology for solar-like oscillations \citep{2010PASP..122..131G,2010ApJ...713L.169C}. It has yielded the detection of gravity-mode period spacings in a red giant \citep{rggmodes,2014A&A...572L...5M}, enabling probes of interior rotation of red giants \citep{rggmoderotation,2012A&A...548A..10M} and distinguishing between hydrogen- and helium-burning cores \citep{rggmodehelium,2012A&A...540A.143M}. It has also permitted the determination of ages and fundamental parameters of main-sequence stars as cool as the Sun and hotter \citep{silvaages}, including planet-hosting stars \citep{huberplanetages,silvaplanetages,2018MNRAS.479.4786V}, revealing the most ancient known planetary system, dating back to the earliest stages of the galaxy \citep{ancientplanets}. By comparing asteroseismic stellar ages to stellar rotation periods, \citet{angusgyro} have shown that gyrochronology models cannot fit the data with a single relation, leading \citet{vansadersgyro} to suggest a qualitative change in dynamo mechanism as stars age through the main sequence. \newpage

@@

In \citet{smear}, we demonstrated a method for extracting precise light curves of bright stars in \kepler and K2, and presented light curves of a small number of variable stars as examples to illustrate this method. In this paper we present smear light curves of all unobserved or significantly under-observed stars brighter than $Kp=9$ in the \kepler field. This sample mostly consists of red giants and hot stars, containing only a few FG dwarfs. We find no transiting planets, but detect \textcolor{red}{$M$}~new eclipsing binaries, and measure solar-like oscillations in 34~red giants. We do not model hot stars or FG dwarfs in great detail, but provide some discussion and initial classification of interesting variability. For eclipsing binaries, we present the results of light-curve modelling to precisely determine their parameters. For the oscillating red giants that constitute the bulk of the sample, we determine the asteroseismic parameters \numax and \Dnu, and therefore stellar masses and \logg measurements. We have also obtained high-resolution optical spectroscopy of 63~objects, predominantly giants, with the Tillinghast Reflector \'{E}chelle Spectrograph (TRES). For the~34 stars with both spectroscopy and asteroseismic parameters we derive fundamental stellar parameters and elemental abundances. These asteroseismic constraints can be compared to those from \gaia, offering the opportunity both to test asteroseismic scaling relations and combine both datasets to refine the benchmark star properties further.

@@

Because the smear data are collected along an entire CCD~column, there is the risk of contamination from sufficiently bright sources. This is especially true in doing asteroseismology of red giants, where the low-amplitude stochastically-excited oscillations can be washed out in a power spectrum by the coherent high amplitude variations of a classical pulsator, even if the background star is much fainter. We can assess the importance of this contamination by considering the differences between odd and even quarters: because the \kepler spacecraft rotates $90^{\circ}$ between successive quarters, any contaminant will lie in the same column as a smear target only every second quarter, falling in the other quarters in the same row but not necessarily the same column. We have therefore generated Lomb-Scargle periodograms \citep{lomb,scargle} of each light curve, clipped for outliers, and considering only odd and even quarters, and visually inspected these for significant differences. In the great majority of cases they closely resemble one another, indicating that contamination is at worst a minor effect. In the case of HD~181878, a red giant, there is clear and significant contamination from an M~giant, as is seen in Figure~\ref{contamination}. Likewise HD~183383 shows two different stars, depending on the quarter: some parts are likely from an ellipsoidal variable with a period of 6.46 days, other parts are from an RR Lyrae pulsator.
